PK object batch mode trial

### 2023-06-15 data-raw/batchMode_trial_gpm.Rmd
facet_data now takes the harmonized variables as arguments for vars()

```{r single_fit}
my_pk <- pk(data = my_predata) +
  facet_data(vars(chemicals_analyzed.dsstox_substance_id,
                  subjects.species_harmonized)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

@@

  coefs <- my_coef(obj = obj) %>%
    dplyr::filter(model %in% model,
                  method %in% method)

@@

  newdata <- newdata %>%
    dplyr::group_by(Route, Media,
                    .add = TRUE) %>%
    mutate(model_fun = case_when(
      type == "conc" ~obj$stat_model[[model]]$conc_fun,
      type == "auc"  ~obj$stat_model[[model]]$auc_fun,
      .default = obj$stat_model[[model]]$conc_fun)) %>%
    reframe(predictions = 
              map(observations,
                  .f = \(x) {
                    x %>%
                      group_by(Time_trans) %>%
                      mutate(Estimate = sapply(coefs_vector,
                                               FUN = model_fun,
                                               time = Time_trans,
                                               dose = ifelse(obj$scales$conc$dose_norm,
                                                             1, Dose),
                                               route = Route,
                                               medium = Media,
                                               simplify = TRUE,
                                               USE.NAMES = TRUE))
                              })) %>%
    unnest(predictions)

@@

my_coefs_update <- coef(my_pk)
my_pred_update <- predict(my_pk, type = "auc",
                          use_scale_conc = TRUE)

my_pred_update %>%
  filter(model == "model_flat",
         Route == "oral",
         Species == "rat", # hamster has a Fgutabs of zero
         method == "L-BFGS-B") %>%
  View("predicted_update")

@@

```{r}
plot_results <- plot(my_pk)

my_tkstats <- get_tkstats(my_pk)
```

>>>>

```{r single_fit}
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference))

@@

  coefs <- coef(obj = obj) %>%
    dplyr::filter(model %in% model,
                  method %in% method)

@@

  newdata <- newdata %>%
    dplyr::group_by(Route, Media,
                    .add = TRUE) %>%
    mutate(model_fun = case_when(
      type == "conc" ~obj$stat_model[[model]]$conc_fun,
      type == "auc"  ~obj$stat_model[[model]]$auc_fun,
      .default = obj$stat_model[[model]]$conc_fun)) %>%
    reframe(predictions = 
              map(observations,
                  .f = \(x) {
                    x %>%
                      group_by(Time_trans) %>% # revise!
                      mutate(Estimate = sapply(coefs_vector,
                                               FUN = model_fun,
                                               time = Time_trans,
                                               dose = ifelse(obj$scales$conc$dose_norm,
                                                             1, Dose),
                                               route = Route,
                                               medium = Media,
                                               simplify = TRUE,
                                               USE.NAMES = TRUE))
                              })) %>%
    unnest(predictions)

@@

my_coefs_update <- coef(my_pk, model = "model_flat", drop_sigma = TRUE)
my_pred_update <- predict(my_pk,
                          use_scale_conc = TRUE)

my_pred_update %>%
  filter(model == "model_2comp",
         Route == "oral",
         Species == "rat", # hamster has a Fgutabs of zero
         method == "L-BFGS-B") %>%
  View("predicted_update")

@@

```{r remaining_methods}
# rmse()
# get_tkstats()
# residuals()
# plot()

my_tkstats <- get_tkstats(my_pk)

plot_results <- plot(my_pk)
